A holomorphic approach to branes in twisted~$M$-theory

### 2022-09-22 fivebranes/index.tex
compilation error
index

The first entry of the AdS/CFT dictionary in traditional treatments is a matching between \textit{supergravity states} and local operators in the CFT.
The goal of this section is to provide constructions of spaces of twisted supergravity states in our eleven-dimensional model, via geometric quantization. The state spaces on $AdS_{7}\times S^{4}$ and $AdS_{4}\times S^{7}$ have a remarkable property---they are naturally modules for certain infinite-dimensional exceptional super Lie algebras. We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.

@@

We now analyze the THF differential $\thfD$ on $\cA^{\bu}_{\mathring M}(L)$ under the above splitting.
\surya{finish}

@@

  \beeqn
  \begin{tikzcd}[row sep = 1 ex]
    + & - \\ \hline
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\partial_{w_i}\}  \ar[r, dotted, "D_{\Omega}"] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \\
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \{\del_{z_i}\} \ar[ur, dotted, "D_{\Omega}"'] \\
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \ar[r, dotted, "D"] \ar[dr, dotted, "D"'] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d z_i\} \\ & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d w_i\} .
\end{tikzcd}
\eeqn
\end{prop}

@@

In \cite{RSW} we have shown that solutions to equations of motion of our eleven-dimensional theory in the twisted $AdS_{7}\times S^{4}$ background recalled in the previous subsection contains the symmetry algebra $\lie{osp}(6|2)$. This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in \ref{hilbert} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.

@@

\brian{enhance to E(3|6)}.
However, we first note that the hilbert space $\cH_{sugra}$ in fact enjoys an action of a much larger symmetry algebra.

@@

For convenience we choose coordinates on the eleven manifold as
\[
\R \times \C^5 = \R_t \times \C^2_w \times \C_z^3 
\]
with $z = (z_i), i=1,2,3$ and $w = (w_a), a=1,2$.
The stack of fivebranes wrap 
\beqn
w_1=w_2=t=0 .
\eeqn
Important for us is to recall that part of the ghost system for our eleven-dimensional theory consists of divergence-free vector fields on $\C^5$ which are locally constant along $\R$.

@@

The twisted supergravity states $\cH_{sugra}^{6d}$ form a representation for $\lie{osp}(6|2)$. 
The weights of twisted supergravity states with respect to the generators of the Cartan subalgebra above are completely determined by the weights of the holomorphic coordinates on $\C^2_w \times \C^3_z$.
These are summarized in table \ref{tbl:sugraM5}.

@@

We enumerate single particle supergravity states via computing the super trace of the operator $q^Y t_1^{h_1} t_2^{h_2} r^h$ acting on $\cH^{6d}_{sugra}$:
\beqn
f^{6d}_{sugra}(t_1,t_2,r,q) = \Tr_{\cH_{sugra}^{6d}} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
\eeqn
The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace. 
That is, we compute the expression

\begin{prop}
\label{prop:sugraindex1}
The single particle index of the space of twisted supergravity states~$\cH_{sugra}^{6d}$ is given by the following expression
\beqn
\label{eqn:sugra_index}
f_{sugra}^{6d} (t_1,t_2, r, q) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
\eeqn
The full (multiparticle) index is defined to be the plethystic exponential 
\beqn
{\rm PExp}\left[f_{sugra}^{6d}(t_1,t_2,r,q)\right] .
\eeqn
\end{prop}

@@

Using the paramterization fo the Cartan given by the variables $y_i,y,\Delta$ we obtain the equivalent expression for the index \eqref{eqn:sugra_index} as 
\beqn
\label{eqn:Kim_sugra}
f_{sugra}^{6d} (y_i, y, q) = \frac{q^4(y_1+y_2+y_3)-q^2(y_1^{-1} + y_2^{-1} + y_3^{-1})+(1-q^3)(yq + y^{-1} q^2)}{(1-y_1 q)(1-y_2 q)(1-y_3 q)(1-yq)(1-y^{-1} q^2)},
\eeqn
We note that this matches exactly with the index computed in \cite[Eq. (3.23)]{Kim:2013nva} with the change of variables.
%\beqn
%t_1 = y_1^{-1} , \quad t_2 = y_3, \quad r = q^{-1/2} y 
%\eeqn

Our formula \eqref{eqn:sugra_index} also matches with \cite[Eq. (3.24)]{Bhattacharya:2008zy} where we use the change of variables
\beqn
q = x^4, \quad t_1 = y_2, \quad t_2 = y_1, \quad r^2 = z .
\eeqn
(Notice the variables $y_1,y_2$ used in \cite{Bhattacharya:2008zy} differ from the variables we introduced in \eqref{eqn:ys}.)
We record a few specializations of this index which we will remark on further in~\S\ref{s:??}.

\parsec 
The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
\[
f_{sugra}^{6d}(q, t_1, t_2=1, r = q^{1/2}) = \frac{q}{(1-q)^2}
\]

This plethystic exponential yields the Macmahon function, which is the character of the vacuum module of the $W_{1+\infty}$-algebra.

\parsec

The specialization $t_1=t_2=r=1$ yields the single particle index
\[
f_{sugra}^{6d} (q, t_1=t_2=r=1) = \frac{3 q^4 - 3 q^2 + 2 q^{3/2} - 2 q^{9/2}}{(1-q)^3 (1-q^{3/2})^2} .
\]

\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $AdS_{7}\times S^{4}$

>>>>

The first entry of the AdS/CFT dictionary in traditional treatments is a matching between \textit{supergravity states} and local operators in the CFT.
The goal of this section is to provide constructions of spaces of twisted supergravity states in our eleven-dimensional model, via geometric quantization. 
The state space on the twisted version of $AdS_{7}\times S^{4}$ has a remarkable property---it is naturally a module for a certain infinite-dimensional exceptional super Lie algebra. 
We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.

@@

We now analyze the THF differential $\thfd$ on $\cA^{\bu}_{\mathring M}(L)$ under the above splitting.
\surya{finish}

@@

  \beqn
  \begin{tikzcd}[row sep = 1 ex]
    + & - \\ \hline
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\partial_{w_i}\}  \ar[r, dotted, "D_{\Omega}"] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \\
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \{\del_{z_i}\} \ar[ur, dotted, "D_{\Omega}"'] \\
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \ar[r, dotted, "D"] \ar[dr, dotted, "D"'] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d z_i\} \\ & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d w_i\} .
\end{tikzcd}
\eeqn
\end{prop}

@@

In \cite{RSW} we have shown that solutions to equations of motion of our eleven-dimensional theory in the twisted $AdS_{7}\times S^{4}$ background recalled in the previous subsection contains the symmetry algebra $\lie{osp}(6|2)$. This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $\lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in~\ref{hilbert} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.

@@

However, we first note that the state space $\cH_{sugra}$ in fact enjoys an action of a much larger symmetry algebra.

\parsec
Surprisingly, at the twisted level this symmetry by the super Lie algebra $\lie{osp}(6|2)$ is enhanced to a symmetry by an infinite-dimensional super Lie algebra called $E(3|6)$. 
This is an exceptional simple super Lie algebra and was classified by Kac in \cite{KacClass}. 
The even part $E(3|6)_{even}$ of this super Lie algebra is a semi-direct product 
\beqn\label{eqn:evenE36}
\Vect(\Hat{D}^3) \oplus \lie{sl}(2) \otimes \cO(\Hat{D}^3) 
\eeqn
where $\Vect(\Hat{D}^3)$ stands for the Lie algebra of (holomorphic) formal vector fields on the three-disk and $\cO(\Hat{D}^3)$ is the algebra of formal power series in three variables.
The odd part $E(3|6)_{odd}$ is 
\beqn\label{eqn:oddE36}
\Omega^{1}(\Hat{D}^3, K^{-1/2}) \otimes \C^2  .
\eeqn
This is the tensor product of the fundamental $\lie{sl}(2)$ representation with the space of one-forms on the formal three-disk twisted by the line bundle $K^{-1/2}$.
For a description of the Lie bracket we refer to \cite{KacClass}.
%The non-obvious Lie bracket is of the form $E(3|6)_{odd} \otimes E(3|6)_{odd} \to E(3|6)_{even}$ and is defined by the composition

The embedding $\lie{osp}(6|2)$ into $E(3|6)$ is described as follows.
The even summand $\lie{sl}(4)$ simply embeds as the constant, linear, and quadratic vector fields which act on a formal neighborhood of $0 \in \C\mathbb{P}^3$.
The even summand $\lie{sl}(2)$ embeds as the constant power series in $\lie{sl}(2) \otimes \cO(\Hat{D}^3)$. 
The odd summand $\C^3 \otimes \C^2$ embeds as the constant one-forms and the other odd summand embeds as the linear one-forms 
\beqn
\frac12 (z_i \d z_j - z_j \d z_i) \otimes w_a
\eeqn
where, here $i \ne j$ and the fundamental $\lie{sl}(2)$ representation is spanned by $w_1,w_2$.
We are leaving out the twist by the $-1/2$ root of the canonical bundle for simplicity.

\begin{prop}
The state space $\cH_{sugra}$ is a representation for $E(3|6)$.
The representation restricts to the original $\lie{osp}(6|2)$ representation under the embedding above.
\end{prop}
\begin{proof}
\brian{Surya can you fill this in}
\end{proof}

@@

We move on to enumerating the state space $\cH_{sugra}$ on the twisted version of $AdS_7 \times S^4$ in terms of the index. 
We choose coordinates on flat space as
\[
\R \times \C^5 = \R_t \times \C^2_w \times \C_z^3 
\]
with $z = (z_i), i=1,2,3$ and $w = (w_a), a=1,2$.
The stack of fivebranes wrap 
\beqn
w_1=w_2=t=0 .
\eeqn
Important for us is to recall that part of the ghost system for our eleven-dimensional theory consists of divergence-free vector fields on $\C^5$ which are locally constant along $\R$.

@@

The twisted supergravity states $\cH_{sugra}$ form a representation for $\lie{osp}(6|2)$. 
The weights of twisted supergravity states with respect to the generators of the Cartan subalgebra above are completely determined by the weights of the holomorphic coordinates on $\C^2_w \times \C^3_z$.
These are summarized in table \ref{tbl:sugraM5}.

@@

We enumerate single particle supergravity states via computing the super trace of the operator $q^Y t_1^{h_1} t_2^{h_2} r^h$ acting on $\cH_{sugra}$:
\beqn
f_{sugra}(t_1,t_2,r,q) = \Tr_{\cH_{sugra}} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
\eeqn
The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace. 
That is, we compute the expression

\begin{prop}
\label{prop:sugraindex1}
The single particle index of the space of twisted supergravity states~$\cH_{sugra}$ is given by the following expression
\beqn
\label{eqn:sugra_index}
f_{sugra} (t_1,t_2, r, q) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
\eeqn
The full (multiparticle) index is defined to be the plethystic exponential 
\beqn
{\rm PExp}\left[f_{sugra}(t_1,t_2,r,q)\right] .
\eeqn
\end{prop}

@@

Using the paramterization fo the Cartan given by the variables $y_i,y,\Delta$ we obtain the equivalent expression for the index \eqref{eqn:sugra_index} as 
\beqn
\label{eqn:Kim_sugra}
f_{sugra} (y_i, y, q) = \frac{q^4(y_1+y_2+y_3)-q^2(y_1^{-1} + y_2^{-1} + y_3^{-1})+(1-q^3)(yq + y^{-1} q^2)}{(1-y_1 q)(1-y_2 q)(1-y_3 q)(1-yq)(1-y^{-1} q^2)},
\eeqn
We note that this matches exactly with the index computed in \cite[Eq. (3.23)]{Kim:2013nva} with the change of variables.
%\beqn
%t_1 = y_1^{-1} , \quad t_2 = y_3, \quad r = q^{-1/2} y 
%\eeqn

Our formula \eqref{eqn:sugra_index} also matches with \cite[Eq. (3.24)]{Bhattacharya:2008zy} where we use the change of variables
\beqn
q = x^4, \quad t_1 = y_2, \quad t_2 = y_1, \quad r^2 = z .
\eeqn
(Notice the variables $y_1,y_2$ used in \cite{Bhattacharya:2008zy} differ from the variables we introduced in \eqref{eqn:ys}.)
%We record a few specializations of this index which we will remark on further in~\S\ref{s:??}.

\parsec 
We consider the specialization of this index 
\beqn
q=r^2, t_2=1 
\eeqn
which is known as the Schur limit.
Applying this limit to \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
\[
f_{sugra}(q, t_1, t_2=1, r = q^{1/2}) = \frac{q}{(1-q)^2}
\]
This plethystic exponential yields the MacMahon function, which is the character of the vacuum module of the $W_{1+\infty}$-algebra.

%\parsec
%
%The specialization $t_1=t_2=r=1$ yields the single particle index
%\[
%f_{sugra}^{6d} (q, t_1=t_2=r=1) = \frac{3 q^4 - 3 q^2 + 2 q^{3/2} - 2 q^{9/2}}{(1-q)^3 (1-q^{3/2})^2} .
%\]
